\documentclass[a4paper]{arthur-letter}

\title{Citibank Group, Inc. Engages in Fascism and Nation State Level Hacking of Ex US Navy SEAL Matthew Woods.}

\author{Matthew Woods F.K.A. Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods F.K.A. Burns}            % Your full name
\linkedin{/in/matthew-woods-75bb721a5}       % Your linkedin
\mail{mattwoods243@outlook.com}       % Your email
\numberphone{+1 808 445 9723}                % Your phone number
\lettitle{Citigroup, Inc. and Wells Fargo participate in fascism and nation state level hacking against a struggling disabled Navy SEAL startup: XignalX, Inc.} % Title of your letter
\site{mattwoods5326.wixsite.com/xignalxincformerlyxi}                       % Your site
\github{XmattwoodsX}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

    \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc. while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. This is across five counties: San Diego, Orange, Santa Clara, Oahu and Hawaii. I think they may have ties to THE Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler and Eichmann of WWII. They lied to me about this since I was born. Target Corporation, local strip malls and police succumb to fascism and try to suppress me in all ways. on top of that, Citigroup Inc. and Wells Fargo launch denial of service attacks to me and XignalX Inc: a struggling startup owned by disabled former US Navy SEALs in Hawaii. Nation state level hacking is apparent.
}
            
    URGENT UPDATE RE Citibank and Wells Fargo
            
    \opening{Dear New York Times,}
            
    From my original letter, "Alphabet Inc. Lies, Blacklists and Conspiracy":

    This is the second attack by Citigroup, Inc. on XignalX, Inc... Both in broad daylight. The first time, I was in Oakland, CA authoring a letter to the New York Times. They hacked, on my then iphone, the Citigroup iOS app, web app, the call center, and, indeed, in person at a branch in Oakland. During the previous episode, the teller at the Citi branch (4101 Piedmont Ave, Oakland, CA 94611) told me the amount of my balance, then immediately got locked out of control from their system. They WOULD NOT GIVE ME MY MONEY... DESPITE ME PROVIDING PROPER ID AT THE SCENE. THEY WOULD NOT RELEASE MY FUNDS. This is a direct connection to the Nazi network that seems to be operating with impunity in America right now, as well as Trump and his network.

    This recent episode is identical. They are doing a repeat of the first attack, but this time I have no ID, a prepaid cell phone and the debit card. They are lying... Just as wells Fargo did back in 2019, when I quit Alphabet Inc. They are doing everything in their power to hack my finances to prevent me from speaking out. It is oppression, by the Nazis, wrt my family and the situation I described in the earlier letter. I advised Citigroup Inc over the phone of impending legal action and the Nazi operative told me that I was warned to shut up. Then they informed me that they would not unblock the card and went dead silent on the other end... As if to give me one final FUCK YOU right to my face. As if they are above the law. I want Citigroup to wind down. They THINK they are "too big to fail"... I BEG TO DISAGREE. I am updating this narrative to include them not responding to stolen debit card calls from me. They continue to hack me via the "fraud" department, as if I have to take this. No one will escalate my pleas to unblock this. Notice of legal action by my startup is imminent as we head into the election. They are contributing to the Hitler cause and I will NEVER forgive them for their recent actions since I opened an account there for the second time. 

    I sit at the big island Hawaii now, under relentless attack from industry and state. They won't stop harassing me because I am speaking out. I must conclude that they are part of the Nazi movement and are cooperating with Alphabet Inc. to disrupt the activities of XignalX, Inc. Barbaric and cruel for a former SEAL owned startup. 

    I have been locked out of all my normal email accounts because my Google hardware 2-factor key was stolen, along with my last meager possessions such as a tent and backpack and Last Will and Testament/Advance Directive. They obviously think they are going to murder me before anyone finds out. The police even joke about that point right in front of my face... Murdering/torturing me. Someone please call these assholes out for Trump's fascist control over the US government/military industrial complex. They have LITERALLY LOCKED ME OUT OF MY CHECKING ACCOUNT ILLEGALLY. THEY WILL NOT ACKNOWLEDGE ME OVER THE PHONE, EVEN FOR A STOLEN DEBIT CARD. THEY ARE NAZIS. FULL STOP.
    
    Update: 23 Jan 2021, after four months without access to my bank account, Citibank was able to verify my account the normal way (i.e. security questions) as if they had not just locked me out for four months. I updated my phone number with them to my current number. Two weeks later, which is today, they initiate another round of illegal holds on my account. This while attempting to make a purchase online for a laptop. Like they do so often, I am greeted by a vacant, belligerently unhelpful customer service team who tell me it is impossible to verify me over the phone with security questions as they had less than one month earlier. They refuse to verify me with all the information at their disposal, including email and my registered phone number. They parrot the same illogical demand that I must have in my possession not only my mobile device (which they have the number) but have a specific variety of service contract with the carrier. They claim that they must have some special kind of phone to verify me and that there is no other way. When installing the Citi mobile app, it sends a text to me, as expected. Yet these dubious alerts about suspicious activity persist. Again, because of their broken systems, I am in hell, in need of food and supplies with no way to access the account. Every day that goes by with them allowed to constrain me this way is like torture. How and why do they insist on playing back and forth like this? I gave them verbal notice of legal action to the supervisor and I am currently seeking counsel to sue them for a pattern of disrupting my life with poverty and suffering. They should be forced to comply with a verification policy that does not require a cell phone contract as these are two very different things. I did not need a cell phone to open the account, I never agreed to be verified this way and it makes no sense that they can trap me like this. Why do they even have such a policy? Perhaps poor people are more likely to have prepaid phone accounts and this is a backhanded way of discriminating against them en mass. The most disturbing part of the arrangement is how this policy materialized during this Trump administration. I construe this as part of the Nazi uprising in the US. Under what circumstances was this electronic hacking scheme hatched? It may be part of a larger plan to wreak havoc on the country by coordinating with other entities once fascism takes root. Apparently all it takes is to combine mobile provider with bank to completely lock someone out of the system. It's illegal, pointing fingers at other entities like my mobile provider. This is the 4th such attack by Citibank, one of the largest/oldest banks.
    
    UPDATE: As I sit here less than one month after the events above, I have yet another illegal hold on my account. I've been on hold for a half an hour for no reason. Hopefully they wont try to lock me out again, like I described. They have disabled the Citi mobile app for me, which I previously used to unlock these type of holds. They did this once before and demanded that I go to a branch. There are no branches on this island. What a load of bullshit. They remind of Wells Fargo doing this to me circa 2019. The intent is to disrupt the customer, as I believe I have been hacked by them at a high level. With all of the commotion in American politics right now, don't forget that Trump is Hitler. 
    
            
            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods FKA Burns}

    \end{letter}
    

\end{document}
